COG-ED Manuscript

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
added some line breaks

      # calculate ANOVA
      hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
                                           dv = "dprime",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)

      # obtain estimated marginal means for ANOVA model
      hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
                                  specs = "level")
      # calculate pairwise comparisons on estimated marginal means
      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)

@@

      # obtain estimated marginal means for ANOVA model
      hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
                                  specs = "level")
      # calculate pairwise comparisons on estimated marginal means
      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)

@@

  # obtain estimated marginal means for ANOVA model
  hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
                              specs = "level")
  # calculate pairwise comparisons on estimated marginal means
  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)

>>>>

      hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
                                           dv = "dprime",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)

      # obtain estimated marginal means for ANOVA model

      hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
                                  specs = "level")

      # calculate pairwise comparisons on estimated marginal means

      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)

@@

      # obtain estimated marginal means for ANOVA model

      hypothesis1b_emm <- emmeans(object = hypothesis1b_rmanova$aov,
                                  specs = "level")
      # calculate pairwise comparisons on estimated marginal means

      hypothesis1b_contrasts <- pairs(hypothesis1b_emm)

@@

  # obtain estimated marginal means for ANOVA model

  hypothesis2a_emm <- emmeans(object = hypothesis2a_rmanova$aov,
                              specs = "level")

  # calculate pairwise comparisons on estimated marginal means

  hypothesis2a_contrasts <- pairs(hypothesis2a_emm)
